---
title: "Developing_week3"
author: "Prem Kiran P"
date: "11/5/2020"
output:
  html_document: default
  word_document: default
---

---
##Variation of mileage with respect to those features of the vehicle.
```{r}
library(plotly)
data(mtcars)
head(mtcars,100)
```
From this car google data set we created some explortaory graphs which can be useful for humans to analyse the relation between these variables such as mileage gives verses
weigth of data such as number of cylinders used, number of gears it has, number of carbs it has. And also we can cheack the relation between horse power to mileage or qsec 
to mileage. We can create ourdesired graph as custmer needed it by taking the insights required for it inti consideration.

In this i plotted the graph between mileage(mpg) verses weight.
```{r}
plot_ly(mtcars) %>%
    add_trace(x = ~mpg, y = ~cyl, type="scatter", mode = "markers",name = "Total No of cyinder", legendgroup = "No of cyinder", 
              marker = list(color = "aquamarine")) %>%
    add_trace(x = ~mpg, y = ~gear, type="scatter", mode = "markers",
              name = "Total No of gears", legendgroup = "Total No of gear", 
              marker = list(color = "yellow4")) %>%
    add_trace(x = ~mpg, y = ~am, type="scatter", mode = "markers",
              name = "Total No of am", legendgroup = "Total No of am", 
              marker = list(color = "#33FF00")) %>%
    add_trace(x = ~mpg, y = ~vs, type="scatter", mode = "markers",
              name = "Total No of vs", legendgroup = "Total No of vs", 
              marker = list(color = "#FF99FF")) %>%
    add_trace(x = ~mpg, y = ~carb, type="scatter", mode = "markers",
              name = "Total No of carbs", legendgroup = "Total No of carb", 
              marker = list(color = "antiquewhite4")) 
```
In the above i used scaterred plot for representing the output data.

And i used different colour code and colour to easily distingush data from other output which is best for humans to see the difference betwenn with naked eye.

There are diffferent ways to produce the output but for this model of output scatter plot is best suitable and i used it to get the desired output for my
peer graded assignment.

This assignment helped me a lot to get know about the colour codes, plots, getting relationsships between data. It is helpful for use for doing this peer and it inceases
the thinkng ability of use.

It took me about 2 to 3 hours to complete this peer graded asiiggnment and it is purely done by me.


